#1. The table below shows the data about shoe size and height. Create a data frame.
#A. Describe the data.
``` {r number1}
df <- data.frame (
  Shoe_size = c(6.5, 9.0, 8.5, 8.5, 10.0, 7.0, 9.5, 9.0, 13.0, 7.5, 10.5, 8.5, 12.0, 10.5, 13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0), 
  Height = c(66.0, 68.0, 64.5, 65.0, 70.0, 64.0, 70.0, 71.0, 72.0, 64.0, 74.5, 67.0, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0),
  Gender = c("F", "F", "F", "F", "M", "F", "F", "F", "M", "F", "M",
             "F", "M", "M", "M", "M", "F", "F", "M", "F", "F", "M", "M", "F", "M", "M", "M", "M")
)
df
```
#B. Create a subset by males and females with their corresponding shoe size and height. What its result? Show the R scripts.

``` {r number1b}
male.subset <- df[df$Gender == "M", c("Shoe_size", "Height")]
female.subset <- df[df$Gender == "F", c("Shoe_size", "Height")]
male.subset
female.subset
```
#c. Find the mean of shoe size and height of the respondents. Write the R scripts and its result.
``` {r number1c}
mean(df$Shoe_size)
mean(df$Height)
```
#D.
#Yes, there is a relationship between the height and shoe size, the taller they are, the longer their shoe size.

#Number2
``` {r number2}
Months <- c("March","April","January","November","January",
"September","October","September","November","August",
"January","November","November","February","May","August",
"July","December","August","August","September","November","February", "April")
factor.months <- factor(Months)
factor.months
```
#3
``` {r number3}
summary(Months)
summary(factor.months)
```
#4
``` {r number4}
DirectionVector <- c("East", "West", "North")
FrequencyVector <- c(1, 1, 3)
FactorData <- factor(c(DirectionVector, FrequencyVector))
NewOrderData <- factor(FactorData,levels = 
                c("East", "West", "North"))
print(NewOrderData)
```
#5
``` {r number5}
student.table <- read.table(file = 'import_march.csv', header = TRUE, sep = ',')
student.table

```

#6.
``` {r num6}
random.num <- sample(1:50, 1)

cat("The chosen number is:", random.num, "\n")

if (random.num == 20) {
  cat("TRUE\n")
} else if (random.num < 1 || random.num > 50) {
  cat("The number selected is beyond the range of 1 to 50\n")
} else {
  cat(random.num, "\n")
}
```
#7.
``` {r num7}
calculate.min.bills <- function(price.of.snack) {
  bill.denominations <- c(1000, 500, 200, 100, 50)
  total.bills <- 0
  
  for (bill in bill.denominations) {
    num.bills.needed <- price.of.snack %/% bill
    price.of.snack <- price.of.snack %% bill
    total.bills <- total.bills + num.bills.needed
  }
  
  cat("Minimum number of bills needed to purchase the snack:", total.bills, "\n")
}

price.of.snack <- 1350
calculate.min.bills(price.of.snack)
```
#8.
#A.
``` {r num8a}
students <- data.frame(
  Name = c("Annie" , "Thea", "Steve", "Hanna"),
  Grade1 = c(85,65,75,95),
  Grade2 = c(65,75,55,75),
  Grade3 = c(85,90,80,100),
  Grade4 = c(100,90,85,90)
)
students
```
#B.
``` {r num8b}
students$Average <- (students$Grade1 + students$Grade2 + students$Grade3 + students$Grade4) / 4

for (i in 1:nrow(students)) {
  average <- (students$Grade1[i] + students$Grade2[i] + students$Grade3[i] + students$Grade4[i]) / 4
  count <- 0
  total_average <- 0
  if (students$Grade4[i] > 90) {
    cat(students$Name[i], "'s average grade this semester is", average, ".\n")
    total.average <- total.average + average
    count <- count + 1
  }
}

if (count > 0) {
  overall.average <- total.average / count
  cat("The overall average for high-achieving students is", overall.average, ".\n")
} else {
  cat("No high-achieving students found.\n")
}
```
#C.
``` {r num8c}
testONE_average <- sum(students$Grade1) / nrow(students)
testTWO_average <- sum(students$Grade2) / nrow(students)
testTHREE_average <- sum(students$Grade3) / nrow(students)
testFOUR_average <- sum(students$Grade4) / nrow(students)

if (testONE_average < 80) {
  cat("The 1st test was difficult.\n")
}
if (testTWO_average < 80) {
  cat("The 2nd test was difficult.\n")
}
if (testTHREE_average < 80) {
  cat("The 3rd test was difficult.\n")
}
if (testFOUR_average < 80) {
  cat("The 4th test was difficult.\n")
}
```
#D.
``` {r num8d}
for (i in 1:nrow(students)) {
  highest.grade <- students$Grade1[i]
  if (students$Grade2[i] > highest.grade) {
    highest.grade <- students$Grade2[i]
  }
  if (students$Grade3[i] > highest.grade) {
    highest.grade <- students$Grade3[i]
  }
  if (students$Grade4[i] > highest.grade) {
    highest.grade <- students$Grade4[i]
  }
  if (highest.grade > 90) {
    cat(students$Name[i], "'s highest grade this semester is", highest.grade, "\n")
  }
}
```